Analysing the 2024 U.S. Presidential Election

### 2024-11-15 paper/paper.qmd
deleted unused column in price_change_lemon_genseng.csv

price_change = read_csv(here::here("data/02-analysis_data/price_change_lemon_ginseng.csv"))
```

@@

>>>>

price_change = read_csv(here::here("data/02-analysis_data/price_change_lemon_ginseng.csv"))

test = read_csv(here::here("data/02-analysis_data/test_data.csv"))
```

@@

# Sample ggplot code to create the point graph
ggplot(price_change, aes(x = nowtime, y = current_price, color = product_name,fill = vendor)) +
  geom_point(alpha = 0.6) +
  labs(x = "Time(Month)",
       y = "Current Price",
       color = "Vendor") +
  facet_wrap(~ vendor, scales = "free_y") +
  theme_minimal() 
```
